### 2018-09-24 ApproxComp/TKDE/sec-conclusion.tex

In this article we have systematiclly introduced approximation computation techniques for efficient and effective big data analytics.
Furthermore, although approximate computation does not put
theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and effectiveness. Indeed, (a) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths/distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks. That is, the design policy of approximate computation is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.

>>>>

In this article we have systematiclly introduced approximation computation techniques for efficient and effective big data analytics.
Furthermore, although approximate computation does not put
theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and effectiveness. Indeed, (a) our query approximation techniques~\cite{ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques~\cite{MaFLWCH16,MaFLWCH17,HuAMH16,DuanAMHH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks. That is, though approximate computation is for a situation where an approximate result is sufficient for a purpose, its design policy is not always to sacrifice effectiveness for efficiency.

%policy is not always to sacrifice effectiveness for efficiency.

%approximate computation  the design policy of is not always to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice for a situation where an approximate result is sufficient for a purpose.

### 2018-09-24 ApproxComp/TKDE/sec-data.tex

For graph embedding, each node is represented as a d-dimensional vector, and the dimensionality $d$ can be large. Hence, such an approach is rather hard to apply to the case of large networks, because the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and because the noises in the embedding seriously impair the accuracy of detected anomalous nodes. Hence, we incorporate data approximation techniques (sampling, graph partitioning techniques, and, moreover, a novel dimension reduction technique) to make the approach more scalable and effective for large networks.

>>>>

Each node in graph embedding is represented as a d-dimensional vector, and the dimensionality $d$ can be large. Hence, such an approach is rather hard to apply to the case of large networks, because the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and because the noises in the embedding seriously impair the accuracy of detected anomalous nodes. Hence, we incorporate data approximation techniques (sampling, graph partitioning, and, moreover, a novel dimension reduction technique) to make the approach more scalable and effective for large networks.
